---
title: "How to Clean and Analyze Your Data"
author: "Yehudis"
date: "05/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "figures/", dev = c("pdf", "png"))
```

Between 2016 and 2018, we have collected data from 1,206 clients who utilized the counseling center at an urban college in a larger university system, for at least one session. We recorded demographic information as provided by the SDS, the number of sessions attended, and their pathology levels on a clinical intake form (the CCAPS-62). 

The study analyzed pre-existing clinical data related to the following questions:

1.	What is the mean number of sessions attended? Does this metric vary by racial or ethnic identity?

2.	Is there a disparity between a racial and/or ethnolinguistic community’s population in the college and their counseling utilization rate?

3.	Is there a disparity between the total CCAPS score among the different racial and/or ethnolinguistic communities? Is there a disparity between the 8 CCAPS subscale scores among the different racial and/or ethnolinguistic communities?

- Before uploading our original data set to R, we removed the data from 26 clients who did not complete the CCAPS-62 questionnaire. This left us with a starting point of 1,180 clients (originally 1,206).

- First, we import and rename our data set. Prior to uploading, we converted our file from a .xlsx (Excel) to a .csv (comma separated values) format, for convenience of using in R. 

```{r}
# Import data file & rename simultaneously

library(readr)
master_data <- read_csv("OG Data Set SLP.csv")
```

Next, we decoded categorical variables that are indicated by numbers in our source code book. While in a software package like SPSS, there is a code book for variable classification, in R we need to indicate what each non-numerical variable is in our global environment. This is most simply done by vectors.

The primary categorical variables that need decoding are ethnicity, gender, and PP (Presenting Problems). The order we type them in corresponds directly to 1, 2, etc.

```{r}
# Decode numerical string variables
## Create a decoder dictionary

ethnicity_code <- c("Black","White","Asian","Latinx","Native American","Multiracial","No Response")

gender_code <- c("Male","Female","Missing/Unknown","Other")

PP_code <- c("Academic workload",
"Adjusting to university",
"Alcohol/drugs",
"Anxiety, fears, nervousness",
"Assertiveness",
"Binging/vomiting",
"Breakup/loss of a relationship",
"Concentration",
"Confusion in beliefs, values",
"Dating concerns",
"Bereavement, general",
"Decisions career/major",
"Depression",
"Developing independence from family",
"Finances",
"Homesick",
"Irritability/anger",
"Making friends",
"Perfectionism",
"Physical health problems",
"Procrastination",
"Problem pregnancy",
"Rape",
"Relationship with family",
"Relationship with peers",
"Relationship with romantic partner",
"Religious, spritual concerns",
"Self-esteem",
"Sexual concerns",
"Sexual identity",
"Sexual orientation",
"Sexually transmitted disease",
"Shyness/ill at ease/isolating (social anxiety)",
"Sleeping problems",
"Starvation, fasting",
"Stress management",
"Study skills problems",
"Suicidal feelings",
"Test/speech performance anxiety",
"Time management",
"Uncertain about future",
"Weight body image",
"Feeling overwhelmed by a number of things",
"Illness in the family",
"Immigration concerns",
"Self-cutting",
"PTSD",
"General lack of motivation, interest in life",
"Generally unhappy or dissatisfied",
"Violent thoughts, feelings, or behaviors",
"Fear of loss of contact with reality",
"Homelessness",
"Bipolar",
"Growing sense of detachment and hopelessness",
"Concerns related to being a member of a minority",
"Emotions out of control, mood swings",
"Intimate partner violence, physical",
"ADHD",
"OCD",
"Loneliness",
"Sextortion",
"Interpersonal Personnel Violence - Sexual",
"Parenting",
"Moving/relocating",
"Adjustment to U.S. - International",
"Concern over arrest/legal",
"Acculturation discrimination",
"Crime victim of violence",
"Schizophrenia",
"Excoriation/dermatillomania",
"Disciplinary",
"Asperger spectrum")
```

We now have to match the decoded variables to their appropriate columns.

We are unsure why - but ethnicity and gender were decoded by the string variables directly in their original cells, while PP_1 was decoded in a new column and the original kept intact. While this does not affect our analysis, we can just keep in mind to use the title of the new column in any graphs or analyses.

```{r}
# Assign a decoded column

master_data$ethnicity <- factor(master_data$ethnicity, 1:7, ethnicity_code)

master_data$gender <- factor(master_data$gender, 1:4, gender_code)

master_data$PP_1 <- factor(master_data$PP1, 1:72, PP_code)
```

Previously, we decoded the variables within a column. Now, we are decoding the actual title of the columns pertaining to the CCAPS-62 items. Note that the CCAPS-62 is graded on a 5-point Likert scale (0-4 in terms of severity) and is therefore a numerical variable.

```{r}
# Decode title of column

CCAPS_44 =	"I feel uncomfortable around people I don't know"
CCAPS_45 =	"I feel irritable"
CCAPS_46 = "I have thoughts of ending my life"
CCAPS_47 = "I feel self conscious around others"
CCAPS_48	= "I purge to control my weight"
CCAPS_49	= "I drink more than I should"
CCAPS_50	= "I enjoy getting drunk"
CCAPS_51 =	"I am not able to concentrate as well as usual"
CCAPS_52	= "I am afraid I may lose control and act violently"
CCAPS_53	= "It's hard to stay motivated for my classes"
CCAPS_29	= "When I drink alcohol I can't remember what happened"
CCAPS_30	= "I feel tense"
CCAPS_31	= "When I start eating I can’t stop"
CCAPS_32	= "I have difficulty controlling my temper"
CCAPS_1	= "I get sad or angry when I think of my family"
CCAPS_33	= "I am easily frightened or startled"
CCAPS_34	= "I diet frequently" 
CCAPS_35	= "I make friends easily"
CCAPS_36	= "I sometimes feel like breaking or smashing things"
CCAPS_37	= "I have unwanted thoughts I can't control"
CCAPS_38	= "There's a history of abuse in my family"
CCAPS_39	= "I experience nightmares or flashbacks"
CCAPS_40	= "I feel sad all the time"
CCAPS_41	= "I am concerned that other people do not like me"
CCAPS_42	= "I wish my family got along better"
CCAPS_43	= "I get angry easily"
CCAPS_2	= "I am shy around others"
CCAPS_3	= "There are many things I am afraid of"
CCAPS_4	= "My heart races for no good reason"
CCAPS_5	= "I feel out of control when I eat"
CCAPS_6	= "I enjoy my classes"
CCAPS_7	= "I feel that my family loves me"
CCAPS_8	= "I feel disconnected from myself"
CCAPS_9	= "I don't enjoy being around people as much as I used to"
CCAPS_10	= "I feel isolated and alone"
CCAPS_11	= "My family gets on my nerves"
CCAPS_12	= "I lose touch with reality"
CCAPS_13	= "I think about food more than I would like to"
CCAPS_14	= "I am anxious that I might have a panic attack while in public"
CCAPS_15	= "I feel confident that I can succeed academically"
CCAPS_16	= "I become anxious when I have to speak in front of audiences"
CCAPS_17	= "I have sleep difficulties"
CCAPS_18	= "My thoughts are racing"
CCAPS_19	= "I am satisfied with my body shape"
CCAPS_20	= "I feel worthless"
CCAPS_21	= "My family is basically a happy one"
CCAPS_22	= "I am dissatisfied with my weight"
CCAPS_23	= "I feel helpless"
CCAPS_24	= "I use drugs more than I should"
CCAPS_25	= "I eat too much"
CCAPS_26	= "I drink alcohol frequently"
CCAPS_27	= "I have spells of terror or panic"
CCAPS_28	= "I am enthusiastic about life"
CCAPS_54	= "I feel comfortable around other people"
CCAPS_55	= "I like myself"
CCAPS_56	= "I have done something I have regretted because of drinking"
CCAPS_57	= "I frequently get into arguments"
CCAPS_58	= "I find that I cry frequently"
CCAPS_59	= "I am unable to keep up with my schoolwork"
CCAPS_60	= "I have thoughts of hurting others"
CCAPS_61	= "The less I eat, the better I feel about myself"
CCAPS_62	= "I feel that I have no one who understands me"
```

We need to reverse the score in some of the CCAPS-62 items. The items we are reversing are positive items whereas the majority of items are scored negatively.

Example of positive item that needs to be reverse-scored: "I make friends easily".

Example of negative item that will retain original value: "I feel that I have no one who understands me".

```{r}
# Reverse score in original column

master_data[,c("CCAPS_06","CCAPS_07","CCAPS_15","CCAPS_19","CCAPS_21","CCAPS_28","CCAPS_35","CCAPS_54","CCAPS_55")] <- 4-master_data[,c("CCAPS_06","CCAPS_07","CCAPS_15","CCAPS_19","CCAPS_21","CCAPS_28","CCAPS_35","CCAPS_54","CCAPS_55")]
```

The sum of the CCAPS-62 values (62 items) totals to a CCAPS score per participant. This will create a new column with the score per participant, as it's a new variable that didn't exist prior.

```{r}
# Add CCAPS score

#44:62 is first to last CCAPS value (range) based on the order that the items were input, as they were not entered in ascending order.
#grep tells me the column number from the name
#row sums adds them up
#"na.rm = TRUE" ignores NA values

master_data$CCAPS_score <- rowSums(master_data[grep("CCAPS_44", colnames(master_data)):grep("CCAPS_62", colnames(master_data))],na.rm = TRUE)
```

The CCAPS-62 is a total pathology score, but is comprised of 8 sub-scales: depression, generalized anxiety, social anxiety, academic distress, eating concerns, family distress, hostility, and substance use. The scores on each sub-scale indicates level of severity in that area for each participant. Clinicians use those scores to see if a client is having particular struggles in an area, and would then address it appropriately in a session. We will get these sub-scores by summing the items that comprise each category.

```{r}
#CCAPS-62 sub-scales

master_data$depression_subscale <- rowSums(master_data[,c(
  "CCAPS_08",
  "CCAPS_09",
  "CCAPS_10",
  "CCAPS_12",
  "CCAPS_20",
  "CCAPS_23",
  "CCAPS_28",
  "CCAPS_37",
  "CCAPS_40",
  "CCAPS_46",
  "CCAPS_55",
  "CCAPS_58",
  "CCAPS_62"
)])

master_data$generalized_anxiety_subscale <- rowSums(master_data[,c(
  "CCAPS_03",
  "CCAPS_04",
  "CCAPS_14",
  "CCAPS_17",
  "CCAPS_18",
  "CCAPS_27",
  "CCAPS_30",
  "CCAPS_33",
  "CCAPS_39"
)])

master_data$social_anxiety_subscale <- rowSums(master_data[,c(
  "CCAPS_02",
  "CCAPS_16",
  "CCAPS_35",
  "CCAPS_41",
  "CCAPS_44",
  "CCAPS_47",
  "CCAPS_54"
)])

master_data$academic_distress_subscale <- rowSums(master_data[,c(
  "CCAPS_06",
  "CCAPS_15",
  "CCAPS_51",
  "CCAPS_53",
  "CCAPS_59"
)])

master_data$eating_concerns_subscale <- rowSums(master_data[,c(
  "CCAPS_05",
  "CCAPS_13",
  "CCAPS_19",
  "CCAPS_22",
  "CCAPS_25",
  "CCAPS_31",
  "CCAPS_34",
  "CCAPS_48",
  "CCAPS_61"
)])

master_data$family_distress_subscale <- rowSums(master_data[,c(
  "CCAPS_01",
  "CCAPS_07",
  "CCAPS_11",
  "CCAPS_21",
  "CCAPS_38",
  "CCAPS_42"
)])

master_data$hostility_subscale <- rowSums(master_data[,c(
  "CCAPS_32",
  "CCAPS_36",
  "CCAPS_43",
  "CCAPS_45",
  "CCAPS_52",
  "CCAPS_57",
  "CCAPS_60"
)])

master_data$substance_use_subscale <- rowSums(master_data[,c(
  "CCAPS_24",
  "CCAPS_26",
  "CCAPS_29",
  "CCAPS_49",
  "CCAPS_50",
  "CCAPS_56"
)])
```

We need to clean our data by removing participants who cannot meaningfully contribute to our analyses. Because our hypotheses are looking at ethnicity, and we cannot come to a statistical conclusion with a sample size of 1 Native American participant, we must remove them from our data. Many participants did not identify their racial/ethnolinguistic identity. Because we are comparing specific racial and ethnolinguistic identities to our CCAPS scores, we must remove unidentified participants from our data set.

```{r}
#delete entire rows by irrelevant ethnicities (no response & native american)

master_data <- master_data[master_data$ethnicity != "No Response",]

master_data <- master_data[master_data$ethnicity != "Native American",]

# We reform the ethnicity factor to account for the removed subjects.

master_data$ethnicity <- factor(master_data$ethnicity)
```

We are left with 809 participants.

Now that we have cleaned our data, it's ready to be analyzed!

We will go through our questions (hypotheses; relaxed language used considering we are analyzing pre-existing data) one by one.

1.	What is the mean number of sessions attended? 

- Does this metric vary by racial or ethnic identity?

- Report # of sessions but use different bars to represent REI

```{r}

# Distribution histogram - Counseling center session attendance (not sorted by REI)

hist(master_data$sessioncount,
main="session count by REI",
xlab="Frequency of Session Count for All Students",
xlim=c(1,70),
col="darkmagenta",
)

mean(master_data$sessioncount)

# Total sum of sessions by each REI

aggregate (master_data$sessioncount, by=list(master_data$ethnicity),FUN=sum)

# Frequency table - sessions by REI

library(tidyverse)
library(dplyr)

SessionCountxREI <- master_data %>%
  group_by(sessioncount, ethnicity) %>%
  summarize(Number_of_Students=length(clientid))

# Distribution histogram - counseling center session attendance sorted by REI

library(ggplot2)

ggplot(SessionCountxREI, aes(x=sessioncount, 
                                  y=Number_of_Students, 
                                  color = ethnicity)) + 
      geom_bar(stat="identity", position = "dodge") +
      facet_wrap(~ethnicity, scales = "free") 

master_data$ethnicity <- as.factor(master_data$ethnicity)
levels(master_data$ethnicity)

# aov(CCAPS_1 ~ ethnicity, master_data)
```

We now want to find out which Presenting Problems were most used among the clients. Then we want to see how the distribution varies by REI.

```{r}
# Create frequency table for Presenting Problem by REI.

PP1xREI <- master_data %>% 
  group_by(ethnicity, PP_1) %>% 
  summarize(Number_of_Students=length(clientid)) %>%
  group_by(ethnicity) %>%
  mutate(total = sum(Number_of_Students)) %>%
  ungroup() %>%
  mutate(Proportion=Number_of_Students/total)
```

We now experiment with a couple of visuals (histograms) to see which style will best tell the story. With 72 PP variables sorted among 5 ethnic/racial groups, it can get a bit crowded.

```{r,fig.width=7.5,fig.height=10}
#PP1 by Ethnicity

PP1_by_Ethnicity <- ggplot(PP1xREI, aes(x=Number_of_Students, 
                                  y=PP_1, 
                                  group=ethnicity,
                                  color = ethnicity)) 

PP1_by_Ethnicity + geom_bar(stat="identity", position = "dodge") + 
  theme_classic(base_size = 15) +
  xlab("Number of Students") +
  ylab("Primary Presenting Problem") + 
  theme(legend.position = c(0.8, 0.1))

```
Take 2. 

```{r,fig.width=10,fig.height=7.5}
#PP1 by Ethnicity
PP1_by_Ethnicity <- ggplot(PP1xREI, aes(y=Number_of_Students, 
                                  x=PP_1, 
                                  group=ethnicity,
                                  color = ethnicity,
                                  fill = ethnicity)) 

PP1_by_Ethnicity + geom_bar(stat="identity", position = "dodge") + 
  theme_classic(base_size = 15) +
  ylab("Number of Students") +
  xlab("Primary Presenting Problem") + 
  theme(legend.position = c(0.7, 0.6)) +
  theme(axis.text.x = element_text(angle = 60, hjust=1))
```
Still too hard to see! Take 3. 

```{r,fig.width=6,fig.height=8}
#PP1 by Ethnicity
PP1_by_Ethnicity <- ggplot(PP1xREI, aes(y=Proportion, 
                                  x=PP_1, 
                                  group=ethnicity,
                                  color = ethnicity,
                                  fill = ethnicity)) 
PP1_by_Ethnicity + geom_bar(stat="identity", position = "dodge") + 
  theme_classic(base_size = 15) +
  ylab("Number of Students") +
  xlab("Primary Presenting Problem") + 
  theme(legend.position = c(0.7, 0.6)) +
  theme(axis.text.x = element_text(angle = 60, hjust=1)) +
   facet_wrap(~ethnicity, ncol = 2)
```

That works if we want to look at REI distibution separately. Let's try stacking for minimalist effect.

```{r StackedPPxEthnicity,fig.width=10,fig.height=7.5}
#PP1 by Ethnicity
PP1_by_Ethnicity <- ggplot(PP1xREI, aes(y=Proportion, 
                                  x=PP_1, 
                                  group=ethnicity,
                                  color = ethnicity,
                                  fill = ethnicity)) 
PP1_by_Ethnicity + geom_bar(stat="identity", position = "stack") + 
  theme_classic(base_size = 11) +
  ylab("Percentage of Students") +
  xlab("Primary Presenting Problem") + 
  theme(legend.position = c(0.7, 0.6)) +
  theme(axis.text.x = element_text(angle = 60, hjust=1))
```
Anxiety was the top concern, followed by depression. Runners up (in order) are stress management, relationship with family, and no response. Honorable mentions are academic workload, breakup/loss of a relationship, and just feeling generally overwhelmed.

-- 

2.	Is there a disparity between a racial and/or ethnolinguistic community’s population in the college and their counseling utilization rate?

We need to measure the percentage breakdown of our sample REI against the percentage distribution in the college. A significant chi-square result would indicate that students are not receiving/seeking out services in the same proportion as their college attendance.

```{r}
# Prepare chi-square data

Diversity <- data.frame(outcome = c("Multiracial","Asian","Latinx","White","Black","Missing"),
                        O = c(5.0,9.0,14.0,20.0,21.0,31.0),
                        E = c(13.9,15.2,16.8,21.8,13.0,19.3))

knitr::kable(Diversity)

Diversity <- Diversity %>%
  mutate(d = O -E) %>%
  mutate(d_sq = d^2) %>%
  mutate(div = d_sq/E)

knitr::kable(Diversity)

# Compute chi-square

sum(Diversity$div)

O <- c(5.0,9.0,14.0,20.0,21.0,31.0)
E <- c(13.9,15.2,16.8,21.8,13.0,19.3)
sum(((O-E)^2)/E)

chisq.test(x=c(5.0,9.0,14.0,20.0,21.0,31.0))
```
As we can see, our chi-square goodness of fit test resulted in a very small p-value of 0.00008016. From this we conclude that there is a substantial disparity between the REI representation at the college and the REI representation at the counseling center.

--

3.	Pathology x racial and ethnolinguistic idenntity

- Is there a disparity between the total CCAPS score among the different racial and/or ethnolinguistic communities? 

- Is there a disparity between the 8 CCAPS sub-scale scores among the different racial and/or ethnolinguistic communities?

To examine this question, we first need to create frequency tables which correspond to each of the toal and sub-scales we will be analyzing. Histograms will help us visualize mean differences between groups.

```{r}
# Create tables for sub-scales and REI

depressionxREI <- master_data %>% 
  group_by((depression_subscale), ethnicity) %>% 
  summarize(Number_of_Students=length(clientid))

generalized_anxietyxREI <- master_data %>% 
  group_by((generalized_anxiety_subscale), ethnicity) %>% 
  summarize(Number_of_Students=length(clientid))

social_anxietyxREI <- master_data %>% 
  group_by((social_anxiety_subscale), ethnicity) %>% 
  summarize(Number_of_Students=length(clientid))

academic_distressxREI <- master_data %>% 
  group_by((academic_distress_subscale), ethnicity) %>% 
  summarize(Number_of_Students=length(clientid))

eating_concernsxREI <- master_data %>% 
  group_by((eating_concerns_subscale), ethnicity) %>% 
  summarize(Number_of_Students=length(clientid))

family_distressxREI <- master_data %>% 
  group_by((family_distress_subscale), ethnicity) %>% 
  summarize(Number_of_Students=length(clientid))

hostilityxREI <- master_data %>% 
  group_by((hostility_subscale), ethnicity) %>% 
  summarize(Number_of_Students=length(clientid))

substance_usexREI <- master_data %>% 
  group_by((substance_use_subscale), ethnicity) %>% 
  summarize(Number_of_Students=length(clientid))

# Make simple histograms for subscales + REI

ggplot(depressionxREI, aes(x=Number_of_Students, 
                                  y=ethnicity)) + 
      geom_bar(stat="identity", position = "dodge") 

ggplot(generalized_anxietyxREI, aes(x=Number_of_Students, 
                                  y=ethnicity)) + 
      geom_bar(stat="identity", position = "dodge") 

ggplot(social_anxietyxREI, aes(x=Number_of_Students, 
                                  y=ethnicity)) + 
      geom_bar(stat="identity", position = "dodge") 

ggplot(academic_distressxREI, aes(x=Number_of_Students, 
                                  y=ethnicity)) + 
      geom_bar(stat="identity", position = "dodge") 

ggplot(eating_concernsxREI, aes(x=Number_of_Students, 
                                  y=ethnicity)) + 
      geom_bar(stat="identity", position = "dodge") 

ggplot(family_distressxREI, aes(x=Number_of_Students, 
                                  y=ethnicity)) + 
      geom_bar(stat="identity", position = "dodge") 

ggplot(hostilityxREI, aes(x=Number_of_Students, 
                                  y=ethnicity)) + 
      geom_bar(stat="identity", position = "dodge") 

ggplot(substance_usexREI, aes(x=Number_of_Students, 
                                  y=ethnicity)) + 
      geom_bar(stat="identity", position = "dodge") 
```
Each 

```{r}
# Ensure ethnicity is properly sorted into levels that can then be used for analyzing.

levels(master_data$ethnicity)

master_data$ethnicity <- ordered(master_data$ethnicity,
                                 levels = c("Black","White","Asian","Latinx","Multiracial"))

library(dplyr)

# Descriptive Statistics - Total Pathology Score by REI

group_by(master_data, ethnicity) %>%
  summarise(
    count = n(),
    mean = mean(CCAPS_score, na.rm = TRUE),
    sd = sd(CCAPS_score, na.rm = TRUE),
    range = range(CCAPS_score, na.rm = TRUE),
  )

library(ggpubr)

# Box plot - Total Pathology Score by REI

ggboxplot(master_data, x = "ethnicity", y = "CCAPS_score", 
          color = "ethnicity", 
          order = c("Black","White","Asian","Latinx","Multiracial"),
          ylab = "Total CCAPS Score", xlab = "Racial and Ethnolinguistic Identity")

# The following plot shows more of the data directly. Too much, perhaps.

ggline(master_data, x = "ethnicity", y = "CCAPS_score",
       add = c("mean_se", "jitter"), 
       order = c("Black","White","Asian","Latinx","Multiracial"),
        ylab = "Total CCAPS Score", xlab = "Racial and Ethnolinguistic Identity")
```
```{r}
# Descriptive Statistics - Depression Sub-Scale Score by REI

group_by(master_data, ethnicity) %>%
  summarise(
    count = n(),
    mean = mean(depression_subscale, na.rm = TRUE),
    sd = sd(depression_subscale, na.rm = TRUE),
    range = range(depression_subscale, na.rm = TRUE),
  )

# Box plot - Depression Sub-Scale Score by REI

ggboxplot(master_data, x = "ethnicity", y = "depression_subscale", 
          color = "ethnicity", 
          order = c("Black","White","Asian","Latinx","Multiracial"),
          ylab = "Depression", xlab = "Racial and Ethnolinguistic Identity")
```
```{r}
# Descriptive Statistics - Generalized Anxiety Sub-Scale Score by REI

group_by(master_data, ethnicity) %>%
  summarise(
    count = n(),
    mean = mean(generalized_anxiety_subscale, na.rm = TRUE),
    sd = sd(generalized_anxiety_subscale, na.rm = TRUE),
    range = range(generalized_anxiety_subscale, na.rm = TRUE),
  )

# Box plot - Generalized Anxiety Sub-Scale Score by REI

ggboxplot(master_data, x = "ethnicity", y = "generalized_anxiety_subscale", 
          color = "ethnicity", 
          order = c("Black","White","Asian","Latinx","Multiracial"),
          ylab = "Generalized Anxiety", xlab = "Racial and Ethnolinguistic Identity")
```
```{r}
# Descriptive Statistics - Social Anxiety Sub-Scale Score by REI

group_by(master_data, ethnicity) %>%
  summarise(
    count = n(),
    mean = mean(social_anxiety_subscale, na.rm = TRUE),
    sd = sd(social_anxiety_subscale, na.rm = TRUE),
    range = range(social_anxiety_subscale, na.rm = TRUE),
  )

# Box plot - Social Anxiety Sub-Scale Score by REI

ggboxplot(master_data, x = "ethnicity", y = "social_anxiety_subscale", 
          color = "ethnicity", 
          order = c("Black","White","Asian","Latinx","Multiracial"),
          ylab = "Social Anxiety", xlab = "Racial and Ethnolinguistic Identity")
```

```{r}
# Descriptive Statistics - Academic Distress Sub-Scale Score by REI

group_by(master_data, ethnicity) %>%
  summarise(
    count = n(),
    mean = mean(academic_distress_subscale, na.rm = TRUE),
    sd = sd(academic_distress_subscale, na.rm = TRUE),
    range = range(academic_distress_subscale, na.rm = TRUE),
  )

# Box plot -Academic Distress Sub-Scale Score by REI

ggboxplot(master_data, x = "ethnicity", y = "academic_distress_subscale", 
          color = "ethnicity", 
          order = c("Black","White","Asian","Latinx","Multiracial"),
          ylab = "Academic Distress", xlab = "Racial and Ethnolinguistic Identity")

```

```{r}
# Descriptive Statistics - Eating Concerns Sub-Scale Score by REI

group_by(master_data, ethnicity) %>%
  summarise(
    count = n(),
    mean = mean(eating_concerns_subscale, na.rm = TRUE),
    sd = sd(eating_concerns_subscale, na.rm = TRUE),
    range = range(eating_concerns_subscale, na.rm = TRUE),
  )

# Box plot - Eating Concerns Sub-Scale Score by REI

ggboxplot(master_data, x = "ethnicity", y = "eating_concerns_subscale", 
          color = "ethnicity", 
          order = c("Black","White","Asian","Latinx","Multiracial"),
          ylab = "Eating Concerns", xlab = "Racial and Ethnolinguistic Identity")

```
The dots above the box plots signify extreme scores (possible outliers). We checked the frequency  table which confirms a few high scores way above the group means.

```{r}
# Descriptive Statistics - Family Distress Sub-Scale Score by REI

group_by(master_data, ethnicity) %>%
  summarise(
    count = n(),
    mean = mean(family_distress_subscale, na.rm = TRUE),
    sd = sd(family_distress_subscale, na.rm = TRUE),
    range = range(family_distress_subscale, na.rm = TRUE),
  )

# Box plot - Family Distress Sub-Scale Score by REI

ggboxplot(master_data, x = "ethnicity", y = "family_distress_subscale", 
          color = "ethnicity", 
          order = c("Black","White","Asian","Latinx","Multiracial"),
          ylab = "Family Distress", xlab = "Racial and Ethnolinguistic Identity")

```

```{r}
# Descriptive Statistics - Hostility Sub-Scale Score by REI

group_by(master_data, ethnicity) %>%
  summarise(
    count = n(),
    mean = mean(hostility_subscale, na.rm = TRUE),
    sd = sd(hostility_subscale, na.rm = TRUE),
    range = range(hostility_subscale, na.rm = TRUE),
  )

# Box plot - Hostility Sub-Scale Score by REI

ggboxplot(master_data, x = "ethnicity", y = "hostility_subscale", 
          color = "ethnicity", 
          order = c("Black","White","Asian","Latinx","Multiracial"),
          ylab = "Hostility", xlab = "Racial and Ethnolinguistic Identity")

```

```{r}
# Descriptive Statistics - Substance Use Sub-Scale Score by REI

group_by(master_data, ethnicity) %>%
  summarise(
    count = n(),
    mean = mean(substance_use_subscale, na.rm = TRUE),
    sd = sd(substance_use_subscale, na.rm = TRUE),
    range = range(substance_use_subscale, na.rm = TRUE),
  )

# Box plot - Substance Use Sub-Scale Score by REI

ggboxplot(master_data, x = "ethnicity", y = "substance_use_subscale", 
          color = "ethnicity", 
          order = c("Black","White","Asian","Latinx","Multiracial"),
          ylab = "Substance Use", xlab = "Racial and Ethnolinguistic Identity")

```
The dots here tell us there is extreme variability in the distribution within groups. 

Report basic demographics: REI, gender, # of credits

General summary of means and range for all variables:
```{r}
summary(master_data)
```
